Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2016-12-20 Manuscript/Manuscript.Rmd

>>>>

**Figure 5: Trends in the black-white life expectancy gap for males between 1969 and 2013 by US state**

```{r figure5, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhite, Sex2 == "Male"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2))
         + facet_wrap(~Census_Region) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") #+
           #geom_text(data = subset(BlackWhite, Year3 == 2010), aes(label = State2), check_overlap = T)
         )
```

**Figure 6: Trends in the black-white life expectancy gap for females between 1969 and 2013 by US state**

```{r figure6, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhite, Sex2 == "Female"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2))
         + facet_wrap(~Census_Region))
```
